\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{kpfonts}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\footskip}{4.2pt}

\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeKVItem}[2]{\item\small{\textbf{#1:} #2}}

\newcommand{\resumeSubheading}[4]{
    \item
    \begin{tabular*}{1\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textbf{\small#2} \\
        \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & \textbf{\small#2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\begin{document}

\begin{center}
    {\Huge \scshape Vo Bui Phu Hung} \\ \vspace{2pt}
    \small (+84) 33-795-5617 $|$  
    \href{mailto:vbph.0512.0@gmail.com}{vbph.0512.0@gmail.com} $|$  
    \href{https://www.linkedin.com/in/jimmyvo0512}{\underline{LinkedIn}} $|$  
    \href{https://github.com/vbphung}{\underline{GitHub}} $|$  
    \href{https://vbphung.github.io/}{\underline{Website}}
    \vspace{-4pt}
\end{center}

\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {University of Science - VNUHCM}
        {2020 - 2024}
        {Bachelor of Science in Computer Science}
        {Advanced Program in Computer Science}
    \resumeItemListStart
        \resumeKVItem{GPA}{3.67/4 (8.31/10)}
        \resumeKVItem{Relevant Courses}{Data Structures \& Algorithms, OOP, Database Management Systems, Computer Hardware, Operating Systems, Mobile Development, 3D Visualization and Game Development}
        \resumeKVItem{Languages}{English - 7.0 IELTS}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Experience}
\resumeSubHeadingListStart
    \resumeSubheading
        {Rawbots Interactive Inc.}
        {Sep 2022 - Sep 2024}
        {Software Engineer}
        {Canada (Remote)}
    \resumeItemListStart
        \resumeItem{Worked (mostly) in a team of 3 to design and implement a scalable microservices-based server architecture.}
        \resumeKVItem{Data Indexing}{Bulk on-chain transactions processing via an injection service from Kafka to MongoDB and Elasticsearch. Provided a thin REST layer for serving indexed data.}
        \resumeKVItem{Content Delivery}{Integrated IPFS for content delivery and efficient decentralized storage of encrypted user-generated content. Built a coordinator dynamically assigning CIDs to external providers with a reward-distribution mechanism.}
        \resumeKVItem{Mobile Development}{Contributed to a social media application by designing/structuring state management (BLoC), implementing push notifications (FCM), and setting up deployment for both Android and iOS.}
        \resumeKVItem{Cryptography}{Designed a blockchain-based end-to-end encrypted (E2EE) chatting feature and provided cryptographic support to client-side teams.}
    \resumeItemListEnd

    \resumeSubheading
        {Gameloft}
        {Feb 2022 - Aug 2022}
        {Unity Developer Intern}
        {Ho Chi Minh City}
    \resumeItemListStart
        \resumeItem{Worked in a team of 8 developers to maintain and implement new features in a launched multiplayer game.}
        \resumeItem{Restructured the hierarchical Prefab system, improving modularity and enabling more efficient and time-saving integration of new content and addons.}
        \resumeItem{Collaborated with back-end developers to build a Downloadable Content (DLC) system leveraging Unity Addressables.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Projects}
\resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{Bitcoin Layer-2 Wallet} $|$ \emph{Graduation Thesis}}
        {Dec 2023 - Aug 2024}
    \resumeItemListStart
        \resumeItem{Supervised by \href{https://www.fit.hcmus.edu.vn/~ttdung/}{\textcolor{blue}{Dr. Tran Trung Dung}} on designing and developing a user-friendly cross-platform desktop cryptocurrency wallet on the Taproot Assets Protocol (TAP) using the Wails framework.}
        \resumeItem{Researched and integrated relevant technologies, including Lightning Network, for a seamless token management.}
        \resumeItem{Conducted research on a secure and decentralized algorithm to improve TAP's cumbersome token exchange flow.}
        \resumeItem{Developed a minimal backend service, enabling seamless token exchange and serving indexed on-chain data. Automated deployment by implementing a CI/CD pipeline.}
    \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Online Code Judge} $|$ \emph{\href{https://github.com/vbphung/code-judge}{\textcolor{blue}{GitHub}}}}
        {Nov 2024}
    \resumeItemListStart
        \resumeItem{Implemented in Go, enabling isolated and multi-language code execution using Docker-in-Docker (DinD).}
        \resumeItem{Utilized the native Docker client to measure execution metrics and employed NATS for asynchronous communication.}
    \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{Coordinator-free Distributed Database} $|$ \emph{\href{https://github.com/vbphung/raft-sql-db}{\textcolor{blue}{GitHub}}}}
        {Feb 2025}
    \resumeItemListStart
        \resumeItem{Used Raft consensus algorithm to ensure strong consistency and fault tolerance among multiple SQLite nodes.}
        \resumeItem{Utilized Gossip protocol in Hashicorp's Memberlist for decentralized cluster membership management.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Technical Skills}
\resumeSubHeadingListStart
    \item
    \resumeItemListStart
        \resumeKVItem{Languages}{Go, TypeScript, C++, SQL, Dart, C\#}
        \resumeKVItem{Frameworks \& Skills}{NestJS, MongoDB, Cassandra, PostgreSQL, Redis, Kafka, Raft, Protocol Buffers, gRPC, Docker, Unity Engine, Flutter, Lightning Network}
        \resumeKVItem{Tools \& Technologies}{Docker, Kubernetes, AWS, Google Cloud Platform, Git, CI/CD}
    \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
